---
title: "Actibase Baseline Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Actibase Baseline Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: refs.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
```

```{r setup}
library(actibase)
```

# Overview

`actibase` is the foundation layer for actigraphy and activity data.
It focuses on raw file reading, standardization, calibration, resampling,
activity counts, non-wear detection, and transformation bookkeeping.

Higher-level summarization, step-count mapping, and downstream statistical
analysis are meant to live in overlay packages that build on top of this
core package.

# Reading data

The package ships with a small GT3X file and a small CWA file under
`inst/extdata`. We will use those examples here.

```{r}
gt3x_file = system.file(
  "extdata",
  "TAS1H30182785_2019-09-17.gt3x.gz",
  package = "actibase"
)
cwa_file = system.file(
  "extdata",
  "ax3_testfile.cwa.gz",
  package = "actibase"
)

gt3x = ab_read_gt3x(gt3x_file, verbose = FALSE)
cwa = ab_read_cwa(cwa_file, verbose = FALSE)

class(gt3x)
names(gt3x)
class(cwa)
names(cwa)
```

The GT3X reader uses `read.gt3x::read.gt3x()` underneath, while the CWA
reader uses `GGIRread::readAxivity()`.

# Standardizing and calibrating

The baseline package keeps the data in a consistent shape:

```{r}
std = ab_standardize_data(gt3x)
cal = ab_calibrate(gt3x, verbose = FALSE)

head(std)
head(cal)
```

The `ab_calibrate()` function is a convenience wrapper around the raw
calibration workflow. It is meant to prepare data for later summary layers
without forcing those layers into this package.

# Resampling

You can resample a three-axis signal to a new sampling rate or to specific
timestamps:

```{r}
resampled = ab_resample(std, sample_rate = 30L)
get_transformations(resampled)

same_times = ab_resample_to_time(
  std,
  times = lubridate::floor_date(std$time, unit = "1 second")
)
get_transformations(same_times)
```

# Counts and wear

The baseline workflow also includes activity-count and non-wear helpers.

```{r}
counts = ab_calculate_counts(resampled, 60L)
wear = ab_calculate_nonwear(counts, method = "choi")

head(counts)
head(wear)
```

Both helpers preserve and extend the `transformations` attribute so that
downstream code can track how the data was derived.

# Transformations

Transformation bookkeeping is explicit:

```{r}
result = dplyr::full_join(counts, wear, by = "time") %>%
  dplyr::mutate(wear = ifelse(is.na(wear), FALSE, wear))

result = set_transformations(
  result,
  c("counts_wear_merge", get_transformations(wear)),
  add = FALSE
)

get_transformations(result)
```

This keeps the baseline pipeline auditable while leaving higher-level
summaries to overlay packages.
