---
title: "Actibase Baseline Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Actibase Baseline Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: refs.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
```

```{r setup}
library(actibase)
library(actiread)
```

# Overview

`actibase` is the foundation layer for actigraphy and activity data.
It focuses on raw file reading, standardization, calibration, resampling,
activity counts, non-wear detection, and transformation bookkeeping.

Higher-level summarization, step-count mapping, and downstream statistical
analysis are meant to live in overlay packages that build on top of this
core package.

# Reading data

The package ships with a small GT3X file and a small CWA file under
`inst/extdata`. We will use those examples here.

```{r}
gt3x_file = acti_example_gt3x()
cwa_file = acti_example_cwa()

gt3x = acti_read_gt3x(gt3x_file, verbose = FALSE)
cwa = acti_read_cwa(cwa_file, verbose = FALSE)

class(gt3x)
names(gt3x)
class(cwa)
names(cwa)
```

The GT3X reader uses `read.gt3x::read.gt3x()` underneath, while the CWA
reader uses `GGIRread::readAxivity()`.

# Standardizing 

The baseline package keeps the data in a consistent shape:

```{r}
std = acti_standardize_data(gt3x)

head(std)
```


# Resampling

You can resample a three-axis signal to a new sampling rate or to specific
timestamps:

```{r}
resampled = acti_resample(std, sample_rate = 30L)
get_transformations(resampled)

same_times = acti_resample_to_time(
  std,
  times = lubridate::floor_date(std$time, unit = "1 second")
)
get_transformations(same_times)
```

